\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-03 k-planar.tex
One small fix

For each $x\in V(T)$, define $S_x := \{v\in V(G): a(v)= x\}$. Since $a:V(G)\to V(T)$ is a function with domain $V(G)$ and range $V(T)$, $\PP:=(S_x : x\in V(T))$ is a sequence of pairwise disjoint sets that cover $V(G)$. Let $J:=G^\SS/\PP$ denote the resulting quotient graph. We consider $V(J)\subseteq V(T)$, where each $x\in V(J)$ is the vertex obtained by contracting $S_x$ in $G^{\SS}$. (Any node $x\in V(T)$ with $S_x=\emptyset$ does not contribute a vertex to $J$.)

@@

\begin{proof}
  For the tree-decomposition $(C_x:x\in V(T))$ of $J$ we use the same tree $T$ used in the tree-decomposition $(B_x:x\in V(T))$ of $H$. For each node $x$ of $T$, we define $C_x$ as follows: $C_x$ contains $x$ as well as every $T$-ancestor $a$ of $x$ such that $J$ contains an edge $ax'$ where $x$ is a $T$-ancestor of $x'$ (including the possibility that $x=x'$).
  \cref{i-ancestor} ensures that, for every edge $ax'\in E(J)$, both $a$ and $x$ are contained in $C_{x'}$.  The connectivity of $T[a]:=T[\{x\in V(T):a\in C_x\}]$ follows from the fact that, for every node $x'\in V(T[a])$, every node $x$ on the path in $T$ from $a$ to  $x'$ is also a node of $T[a]$.  Therefore $(C_x:x\in V(T))$ is indeed a tree-decomposition of $J$.

>>>>

For each $x\in V(T)$, define $S_x := \{v\in V(G): a(v)= x\}$. Since $a:V(G)\to V(T)$ is a function with domain $V(G)$ and range $V(T)$, $\PP:=\{S_x : x\in V(T)\}$ is a partition of $V(G)$. Let $J:=G^\SS/\PP$ denote the resulting quotient graph. We consider $V(J)\subseteq V(T)$, where each $x\in V(J)$ is the vertex obtained by contracting $S_x$ in $G^{\SS}$. (Any node $x\in V(T)$ with $S_x=\emptyset$ does not contribute a vertex to $J$.)

@@

\begin{proof}
  For the tree-decomposition $(C_x:x\in V(T))$ of $J$ we use the same tree $T$ used in the tree-decomposition $(B_x:x\in V(T))$ of $H$. For each node $x$ of $T$, we define $C_x$ as follows: $C_x$ contains $x$ as well as every $T$-ancestor $a$ of $x$ such that $J$ contains an edge $ax'$ where $x$ is a $T$-ancestor of $x'$ (including the possibility that $x=x'$).
  \cref{i-ancestor} ensures that, for every edge $ax'\in E(J)$, both $a$ and $x$ are contained in $C_{x'}$\todo{Do we mean $C_x$ here?}.  The connectivity of $T[a]:=T[\{x\in V(T):a\in C_x\}]$ follows from the fact that, for every node $x'\in V(T[a])$, every node $x$ on the path in $T$ from $a$ to  $x'$ is also a node of $T[a]$.  Therefore $(C_x:x\in V(T))$ is indeed a tree-decomposition of $J$.
